The Implications of Disk Oscillations for Dynamical Analysis in the \textit{Gaia} Era

### 2019-06-30 paper/ms.tex
Update discussion of pre-Gaia results

The true Galactic potential is not strictly axisymmetric. This has been known
for some time \citep[e.g.,][]{1957AJ.....62...93K,2009MNRAS.396L..56M,
2012ApJ...750L..41W}, but with the vast improvement in the quality of
phase-space measurements due to \textit{Gaia} the assumption of axisymmetry is
increasingly inadequate \citep[e.g.,][]{2018Natur.561..360A,
2019MNRAS.485.3134L}. Even if this assumption were close enough for many
purposes, the parameters used in axisymmetric models of the Galactic potential
may be inadequately constrained by current observations.

>>>>

\textbf{The true Galactic potential is not strictly axisymmetric, beyond even
the typically-quoted gas clouds, spiral arms, and bar(s). The presence of disk
oscillations has been known for some time, observed in 1957 for H~\textsc{i}
in the outer disk \citep{1957AJ.....62...93K}. The presence of a North-South
asymmetry in stellar number density and velocity in the solar neighborhood has
been found in SDSS data \citep{2012ApJ...750L..41W}, and in velocity in the
LAMOST survey \citep{2013ApJ...777L...5C}, and RAVE data
\citep{2013MNRAS.436..101W}. Beyond the solar neighborhood, low-latitude
overdensities have been observed, e.g., the Monoceros Ring
\citep{2002ApJ...569..245N, 2003MNRAS.340L..21I, 2003ApJ...594L.119C,
2014ApJ...791....9S, 2016ApJ...825..140M}, an overdensity in the direction of
the Triangulum and Andromeda galaxies \citep{2007ApJ...668L.123M,
2014ApJ...793...62S, 2015ApJ...801..105X, 2015MNRAS.452..676P} and A13
\citep{2010ApJ...722..750S, 2017ApJ...844...74L}, and in the direction of the
Galactic Center \citep{2014Natur.509..342F}. There is evidence that these
stellar populations originated from the disk \citep{2018ApJ...854...47S,
2018Natur.555..334B}. See, e.g., \citet{2018MNRAS.481..286L} for a discussion
of these observations.}

\textbf{With the vast improvement in the quality of phase-space measurements
due to \textit{Gaia} the assumption of axisymmetry is increasingly inadequate
\citep[e.g.,][]{2018Natur.561..360A, 2019MNRAS.485.3134L}. The presence of the
phase-space spiral itself is evidence of disk oscillations
\citep{2018Natur.561..360A}, but the fact that its strength changes across the
disk is further evidence \citep{2019MNRAS.486.1167B}. Even if the axisymmetric
assumption were close enough for many purposes, the parameters used in
axisymmetric models of the Galactic potential may be inadequately constrained
by current observations.}
